When does vapor pressure deficit drive or reduce evapotranspiration?\footnote{Primary Research Article}

### 2018-03-01 doc/paper/vpd_et_paper.tex
about to submit

\journalname{Global Change Biology}

@@

\begin{keypoints}
\item hydrometeorology, evapotranspiration, aridity, vapor pressure deficit, Clausius-Clapeyron relation, plant physiology, stomatal response
\end{keypoints}

>>>>

\journalname{Global Change Biology: When does VPD drive or reduce ET?}

@@

\begin{keypoints}
\item ecohydrology, evapotranspiration, aridity, vapor pressure deficit, Clausius-Clapeyron relation, plant physiology, stomatal response
\end{keypoints}
